TacticToe: Learning to Prove with Tactics

### 2018-02-20 tactictoe_jv.tex
3 more spotted grammar

\subsection{Methodology}
The evaluation imitates the construction of the library: For each theorem only
the previous human proofs are known. These are used as the learning base for
the predictions.
To achieve this scenario we re-prove all theorems during a modified build of
\holfour.
As theorems are proved, their tactical proofs and their statements are
recorded and included in the training examples.
For each theorem we first attempt to run the \tactictoe search with a time
limit of 60 seconds before processing the original proof script.
In this way, the fairness of the experiments is guaranteed by construction:
only previously declared \sml variables (essentially tactics, theorems and 
simpsets) are accessible to \tactictoe.

@@

\paragraph{Reconstruction}
Tactic proofs produced by \tactictoe during this experiment are all verifiable
in \holfour. By the design of the proof search, reconstruction of \tactictoe
proof succeeds, unless one of the tactic modifies the state of \holfour in a
way that changes the behavior of a tactic used in the final proof. Such an
event has not yet occurred.
More details on how a proof is extracted from the search tree is given in
Section~\ref{sec:proofdisplay}.
Comparatively, we achieve a reconstruction rate of 95 percent for \eprover,
by calling \metis for 2.0 seconds with the set of theorems necessary for 
in \eprover's proof as argument.

@@

\textsf{ML4PG}~\cite{DBLP:journals/corr/abs-1212-3618,DBLP:journals/mics/HerasK14}
groups related proofs using clustering
algorithms. It allows \coq users to inspire themselves from similar proofs and
notice duplicated proofs. Comparatively, our predictions comes from a much more
detailed description of the target goal. \tactictoe can also organize the 
predictions to produce verifiable proofs and is not restricted to user 
advice.
%However, we simply create a single label for each tactic call whereas each of
%its
%arguments is treated independently in \textsf{ML4PG}.
%Our choice is motivated by the k-NN algorithm already used in
%\holyhammer for the a of theorems.
%, which can be easly adapted to the selection of tactics but would be improved
%by a
%version that can learn to predict tactics and their arguments independently.

>>>>

\subsection{Methodology}
The evaluation imitates the construction of the library: For each theorem only
the previous human proofs are known. These are used as the learning base for
the predictions.
To achieve this scenario we re-prove all theorems during a modified build of
\holfour.
As theorems are proved, their tactical proofs and their statements are
recorded and included in the training examples.
For each theorem we first attempt to run the \tactictoe search with a time
limit of 60 seconds before processing the original proof script.
In this way, the fairness of the experiments is guaranteed by construction:
only previously declared \sml values (essentially tactics, theorems and 
simpsets) are accessible to \tactictoe.

@@

\paragraph{Reconstruction}
Tactic proofs produced by \tactictoe during this experiment are all verifiable
in \holfour. By the design of the proof search, reconstruction of \tactictoe
proof succeeds, unless one of the tactic modifies the state of \holfour in a
way that changes the behavior of a tactic used in the final proof. Such an
event has not yet occurred.
More details on how a proof is extracted from the search tree is given in
Section~\ref{sec:proofdisplay}.
Comparatively, we achieve a reconstruction rate of 95 percent for \eprover,
by calling \metis for 2.0 seconds with the set of theorems used
in \eprover's proof as argument.

@@

\textsf{ML4PG}~\cite{DBLP:journals/corr/abs-1212-3618,DBLP:journals/mics/HerasK14}
groups related proofs using clustering
algorithms. It allows \coq users to inspire themselves from similar proofs and
notice duplicated proofs. Comparatively, our predictions come from a much more
detailed description of the target goal. \tactictoe can also organize the 
predictions to produce verifiable proofs and is not restricted to user 
advice.
%However, we simply create a single label for each tactic call whereas each of
%its
%arguments is treated independently in \textsf{ML4PG}.
%Our choice is motivated by the k-NN algorithm already used in
%\holyhammer for the a of theorems.
%, which can be easly adapted to the selection of tactics but would be improved
%by a
%version that can learn to predict tactics and their arguments independently.
